---
title: Hyacinthe Sarr - STA 9750
---

# Welcome to my website

I’m a graduate student in the **MS in Statistics (Data Science)** at Baruch College. This site hosts coursework and projects for STA 9750 – Software Tools for Data Analysis.Previously, I worked as an **Underwriter** at **Fora Financial**, focusing on financial analysis and risk assessment. I hold a **Bachelor's degree in Actuarial** Science from Baruch College and a **Bachelor’s in International Business** from Université Paul Valéry (Montpellier, France).


- Interests: Statistical Analysis, Risk Analysis, Predictive Modeling, Probability Theory.

## Connect with me

Linkedin: [Hyacinthe Sarr](https://www.linkedin.com/in/hsarr2802/)

### Baruch College
```{r}
#| echo: false
#| message: false
#| warning: false

if (!require("leaflet")) {
  options(repos = c(CRAN = "https://cloud.r-project.org"))
  install.packages("leaflet")
  stopifnot(require("leaflet"))
}

baruch_longitude <- -73.98333
baruch_latitude  <-  40.75028

leaflet() |>
  addTiles() |>
  setView(baruch_longitude, baruch_latitude, zoom = 17) |>
  addPopups(baruch_longitude, baruch_latitude,
            "Here is <b>Baruch College</b>!")
```


### Université Paul Valéry
```{r}
#| echo: false
#| message: false
#| warning: false

montpellier_longitude <- 3.8695
montpellier_latitude  <- 43.6333

leaflet() |>
  addTiles() |>
  setView(montpellier_longitude, montpellier_latitude, zoom = 16) |>
  addMarkers(lng = montpellier_longitude,
             lat = montpellier_latitude,
             popup = "Here is <b>Université Paul Valéry</b> (Montpellier)!")
```


```{r}
#| include: false
1+1
```
--------------
Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`

