---
title: Hyacinthe Sarr - STA 9750
---

# Welcome to my website

I'm a graduate student in the **MS Statistics (Data Science)** at Baruch College. This website hosts all my coursework submission as well as the projects for **STA9750 - Software Tools for Data Analysis**. Before starting my MS in Statistics, I worked as an **Underwriter** at **Fora Financial** where I gained experience in financial analysis and risk assessment. I also graduated from Baruch College with a **BA in Actuarial Science**.

- Interests: Statistical Analysis, Analysis, Predictive Modeling, Probability Theory.

## Connect with me

Linkedin: [Hyacinthe Sarr](https://www.linkedin.com/in/hsarr2802/)

```{r}
#| echo: false
#| message: false
#| warning: false

if (!require("leaflet")) {
  options(repos = c(CRAN = "https://cloud.r-project.org"))
  install.packages("leaflet")
  stopifnot(require("leaflet"))
}

baruch_longitude <- -73.98333
baruch_latitude  <-  40.75028

leaflet() |>
  addTiles() |>
  setView(baruch_longitude, baruch_latitude, zoom = 17) |>
  addPopups(baruch_longitude, baruch_latitude,
            "Here is <b>Baruch College</b>!")
```

```{r}
#| include: false
1+1
```
--------------
Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`

