---
title: "Mini-Project 03 - Visualizing and Maintaining the Green Canopy of NYC"
author: "Hyacinthe Sarr"
editor:
    mode: source
format:
  html:
    toc: true
    toc-title: "Contents"
    number-sections: false
    theme: zephyr
    css: styles.css
    code-fold: true
    code-summary: "Show code"
    mainfont: Georgia
    embed-resources: true
execute:
  warning: false
  message: false
---

## Introduction

A suitable introduction goes here. In this mini-project, I intend to demonstrate
my skills at API Use/Big Data/Geospatial Data in an analysis of Municipal Data/Spatial Analysis data.

## Data Acquisition and Preparation

Code related to Data Acquisition and Preparation goes here.

Remember that code blocks look like this: 

```{r}
# Your code goes in chunks like this
library(tidyverse) # You will want this line for almost all MPs
x <- 1 + 2 + 3
```

and you can then print variables from chunks: 

```{r}
x
```

or inline, like this: $x$ is `r x`.

## Exploratory Analysis

Code related to Exploratory Data Analysis goes here. This may include
exploratory graphics, instructor-provided exploratory questions, or other
similar elements. 

## Final Insights and Deliverable

Code related to the final deliverable of the assignment goes here. 



------------------------------------------------------------------------

This work ©2025 by Actudata77 was initially prepared as a Mini-Project for
STA 9750 at Baruch College. More details about this course can be found at
[the course site](https://michael-weylandt.com/STA9750) and instructions for
this assignment can be found at 
[MP #03](https://michael-weylandt.com/STA9750/miniprojects/mini03.html)
